### 2021-08-05 paper/paper.tex
draft of the setup section

FLUXO\footnote{\url{https://gitlab.com/project-fluxo/fluxo}} is an open source
MPI Fortran code implementing discontinuous Galerkin methods on unstructured hex
meshes in three space dimensions for advection diffusion equations. It also
implements the same kind of modern DG methods based on flux differencing
to achieve entropy conservation/dissipation or kinetic energy preservation.
At the same time, both codes also have features the other one does not, \eg,
parabolic equations and MPI in FLUXO or multiple mesh types and more physics setups
in \trixi. Nevertheless, both \trixi and FLUXO share a common set of features,
enabling a reasonable comparison of their performance.

@@

\todo{TODO: Andrew, could you please describe the setups that you used? %TODO Andrew
\begin{itemize}
  \item Physical setup
  \item Numerical methods/parameters
  \item Software versions, compiler \etc
  \item Hardware
\end{itemize}}

>>>>

FLUXO\footnote{\url{https://github.com/project-fluxo/fluxo}} is an open source
MPI Fortran code implementing discontinuous Galerkin methods on unstructured hex
meshes in three space dimensions for advection-diffusion equations. It also
implements the same kind of modern, flux differencing DG methods 
to achieve entropy conservation/dissipation or kinetic energy preservation.
At the same time, both codes have features the other does not, \eg,
approximation capabilities for parabolic equations and MPI in FLUXO 
or multiple mesh types and more physics setups in \trixi. Nevertheless, 
both \trixi and FLUXO share a common set of features, \eg, high-order DG 
methods on 3D curvilinear meshes, that enables a reasonable comparison of their performance.

@@

For the problem setup we consider a periodic box of the domain $[-1,1]^3$ with four elements in each
spatial direction. To make the mesh curvilinear, the interior of the box is heavily warped
by a combination of sine and cosine functions~\cite{chan2019efficient}. To integrate up to the
final time $t=1.0$, both codes use the five-stage, four-order low-storage explicit
Runge-Kutta method of Carpenter and Kennedy~\cite{CarpenterKennedy1994}.
A stable explicit time step is adaptively computed according to the local maximum wave
speed, the relative grid size, and an adjustable Courant-Friedrichs-Lewy (CFL)
coefficient $\text{CFL}\in(0,1]$~\cite{gassner2011}. For the performance computations presented herein
we fix this coefficient to be $\text{CFL}=0.5$.

We compare the performance of FLUXO and \trixi for two smooth nonlinear problems,
a manufactured solution for the 3D compressible Euler equations and Alfv\'{e}n wave propagation for
the 3D ideal MHD equations~\cite{altmann2012}. These initial conditions, available in FLUXO and
\trixi, are typically used for the purpose of demonstrating the high-order accuracy and convergence properties
of the frameworks.

For these comparisons we examine the performance of FLUXO and \trixi for the weak
form as well as flux differencing implementations of the DG solver. For the weak form simulations we compute
the coupling between elements with a Harten-Lax-van Leer (HLL) numerical surface flux function~\cite{Toro2009,li2005hllc}.
For the flux differencing solver, that introduces an additional numerical volume flux function, we use an entropy-conservative flux
function in both the volume and at the surface. For the compressible Euler equations this flux is also kinetic energy preserving~\cite{ranocha2020icosahom}
while for the ideal MHD equations it is kinetic and magnetic energy preserving~\cite{hindenlang2019}. We note that both ideal MHD implementations
contain additional computational overhead due to nonconservative terms necessary for the numerical approximation 
to remain entropy consistent~\cite{bohm2020}. Additionally, the weak form DG solver type is recovered if one uses a central flux 
in the volume of the flux differencing DG solver, albeit with additional computational cost.

All simulations for the performance comparison were run on the High Performance Computing (HPC) system Tetralith 
provided by the Swedish National Infrastructure for Computing (SNIC). 
Each node of Tetralith has two sockets, each with an Intel(R) Xeon(R) Gold 6130 @ 2.10GHz with 96GiB of memory. 
FLUXO was compiled using the Intel compiler suite v18.0.3 and \trixi used Julia v1.6.1. 
The serial performance results we run on a single core. 
We ran each configuration of a particular physical setup, polynomial degree, and solver type
for each code five times, taking the smallest value from each in the comparison results.

To assess the performance of the two codes we vary the polynomial degree (polydeg) in the range $[3,15]$.
This corresponds to considering DG approximations of (increasing) high-order spatial accuracy, from fourth up to sixteenth order.
The metric we use to analyze and compare FLUXO and \trixi simulations is a performance index (PID) that
measures the time required to advance a single degree of freedom (DOF) from one stage of the explicit Runge-Kutta
time integration scheme to the next. It is computed as
\begin{equation}
\label{eqn:pid}
\text{PID} = \frac{\text{wall-clock-time}}{\#\text{time steps}\cdot\#\text{elements}\cdot(\text{polydeg}+1)^3}.
\end{equation}
